
---
title: "Dickinson Family Library progress meter"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: readable
  word_document: default
  pdf_document: default
---
```{r, originalRequest,eval=FALSE, include=FALSE}

2023-06-08
Dear Bill,

I’m writing to ask if there might be any wiggle-room that would enable an increase in the number of Dickinson Family Library books going through D40. Jene told Christine when she picked up the last batch that they could only handle 750 pages a month. At that rate—and assuming that indeed nothing like the pandemic again intervenes—the project will take some 9.5 years to complete (2034). We have an estimated 86,847 pages to go, those books only suitable to D40.

Given lack of staff in D40, we have already shifted as much work as possible to D20 workflow, and will finish those books around the end of this calendar year. I understand the new scanner didn’t work out. If I should investigate outside vendors, such as NEDCC, to take on this work please let me know if that’s an acceptable alternative. Dickinson is our highest-profile collection, and the digital work already completed is both highly used, and highly appreciated within the scholarly community. I would dearly love to get this project finished before I retire—and while that may not be in the short term, it is certainly going to happen before 2034!

I do understand that EDIBA projects are to be given priority, and I don’t want to compromise that important work. From a Houghton perspective, as a male-dominated collection, Dickinson (and other women writers) are definitely an equity issue. I’d appreciate your help in trying to find a way to move this forward at a faster pace.

With appreciation for your time and attention,

Leslie

############################################
#### 06/27/2024 from Christine Jacobson ####
############################################

Hi Bill!

We now have some updated numbers for the studio and the lab workflow. I think there’s a lot of good news here; though depending on how we can handle the periodicals, there might still be a long road ahead with the studio side. I will bring a few examples next time I see Joe and get his perspective on whether they can be done at the lab or not. I hope this is helpful for assessing a reasonable timeline.  

Amount of call numbers and pages left (estimated)

Studio-designated titles

36 call numbers left
15, 124 pages
Currently sending: 600 pages per month, with pick up and drop offs happening every 2-3 months
Lab-designated titles

88 call numbers left
47,713 pages left
Currently sending 4k pages per batch, with pick up and drop offs happening once a month.
To-be Designated titles (will consult with Joe Cavallo)

6 call numbers left, but includes 56 vols of periodicals
223,050 pages left
Titles to-be treated at Weissman before imaging (will assign them Studio/Lab after treatment)

18 call numbers left
97, 440 pages left
Total call numbers left to be digitized: 148 

Total pages left to be digitized: 171,971

____________________________________________________________________________________________

Potential Timelines

Lab

at a rate of 4k/month we could complete digitization of lab-designated books in 12 months
Studio

At a rate of 600/month we could complete digitization of studio-designated books in 25 months
Periodicals

This material constitutes 97, 440 pages
It is not yet clear whether we can send this material to the Studio or the Lab; will review with Joe Cavallo. The majority of it is in poor condition.

Best case scenario: at a rate of 4k/month this material will add 25 months to the project, or a little more than 2 years

Worst case scenario: at a rate of 600/month this material will add 162 months to the project, or 13.5 years

Other Potential Challenges:

Modern will need to hire and train a new LHT in the summer of 2024 after the departure of our current department assistant who handles all 
metadata

Christine will go on maternity leave from November 2024-April 2025.

The pace at the Studio continues to be unpredictable and it is unclear at what pace we’ll be able to digitize the 36-42 call numbers left
 
Christine

```


```{r loadPackages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls()) # clear env vars

pkgs.inst <- as.data.frame(installed.packages(noCache = TRUE)) # list of installed R packages

pkgs.load <- c( # default list of packages to load
   # "DiagrammeR",
   # "DiagrammeRsvg",
   # "digest",
   "dplyr",
   "DT", # https://rdrr.io/cran/DT/
   # "esquisse", # GUI ggplot 
   # "formattable",
   "ggplot2",
   # "glue", # join strings neatly
   "htmlTable",
   # "janitor", # clean-up messy col names janitor::clean_names()
   "jsonlite",
   "lubridate",
   # "magrittr",
   "ganttrify",
   "mime",
   # "officer",
   "pandoc",
   "plan", # for creation of gantt charts
   "plotly",
   # "RColorBrewer",
   "RCurl",
   "readr",
   "readxl",
   "rsvg",
   "Rtools",
   "scales",
   "stats",
   # "tidylog",
   "tidyr",
   "tidytext", # pull apart text data, count elements
   "tidyverse",
   # "tsibble", # time series data
   "utf8",
   # "vroom", # loads data fast
   # "webshot",
   "xml2",
   "xtable"
)
#
idx <- pkgs.load %in% pkgs.inst$Package == FALSE # index of packages that need to be installed
# pkgs.load[idx]
if(sum(idx) > 0){
  install.packages(pkgs.load[idx],
                   dependencies = TRUE,
                   repos = "http://stat.ethz.ch/CRAN/")
  } # if at least one package needs installing, run.
lapply(pkgs.load, require, character.only = TRUE) # require packages be loaded into current env
##
timezone <- "US/Eastern" #Set timezone # set TZ
if(is.na(Sys.timezone()) == TRUE){
  Sys.setenv(TZ=timezone)
}
##
os <- .Platform$OS.type
os <- Sys.info()[[1]][1] #windows linux # identify OS
#
options(scipen=999)
# end
# <style>th,td{padding:5px 5px 5px 5px;}</style>


```

```{r loadData, include=FALSE}

# ServiceDetails <- read_excel("P:/R/data/IS_ServiceDetails.xlsx")
#########################################
## compensate for platform differences ##
df.source.file.name <- "IS_ServiceDetails.xlsx"
mac.path <- "../data/"
win.path <- "P:/R/data/"
lnx.path <- "../data/"
if(os == "Darwin"){
  df.source.file.path <- mac.path
  df.source.full.path <- paste0(df.source.file.path,df.source.file.name)
} else if(os == "Windows"){
  df.source.file.path <- win.path
  df.source.full.path <- paste0(df.source.file.path,df.source.file.name)
} else if(os == "linux"){
  df.source.file.path <- lnx.path
  df.source.full.path <- paste0(df.source.file.path,df.source.file.name)
}
## compensate for platform differences ##
#########################################
ServiceDetails <- read_excel(df.source.full.path)

class(ServiceDetails$`PhotoduplicationDate (Day-Month-Year)`)
ServiceDetails$`PhotoduplicationDate (Day-Month-Year)` <- as.Date(ServiceDetails$`PhotoduplicationDate (Day-Month-Year)`)


```

```{r vars, include=FALSE}

EDFL <- ServiceDetails # establish the EDFL dataframe

min.date <- min(EDFL$`PhotoduplicationDate (Day-Month-Year)`)
max.date <- max(EDFL$`PhotoduplicationDate (Day-Month-Year)`)
start.date <- as.Date("2023-06-08") # needed? 
today <- format.Date(Sys.time(),"%Y-%m-%d")
start.measure.date <- as.Date("2024-06-27")

worflow.not.yet.assigned.images <- 223050 # per Christine Jacobson, 6/27/24
D20.images.remaining <- 47713 # per Christine, 6/27/24, here i assume all pages without a designated workflow (D20 or D40) are to be queued for D20, even though we know some portion will go to D40.
D40.images.remaining <- 15124
# images.remaining.as.of.start.measure.date <- as.numeric(86847) # per L. Morris, 06/08/2023
pageimages.to.be.treated.WPC <- 97440

# images.remaining.as.of.start.measure.date <- as.numeric(worflow.not.yet.assigned.images + D20.images.remaining + D40.images.remaining + pageimages.to.be.treated.WPC) # per C. Jacobson, 06/27/2024

images.remaining.as.of.start.measure.date <- as.numeric(D20.images.remaining + D40.images.remaining + pageimages.to.be.treated.WPC) # per C. Jacobson, 06/27/2024, removed count of workflow images not yet assigned

```
<!-- ### Scrap paper -->

<!-- * Studio-designated titles (`r D40.images.remaining`) + Lab-designated titles (`r D20.images.remaining`) + To-be Designated titles (`r worflow.not.yet.assigned.images`) = `r prettyNum(D40.images.remaining + D20.images.remaining + worflow.not.yet.assigned.images, big.mark = ",")` images. -->

<!-- * Studio-designated titles (`r D40.images.remaining`) + Lab-designated titles (`r D20.images.remaining`) + Titles to-be treated at Weissman before imaging (`r pageimages.to.be.treated.WPC`) = `r prettyNum(D40.images.remaining + D20.images.remaining + pageimages.to.be.treated.WPC, big.mark = ",")` images. -->

<!-- * 171971 - `r D40.images.remaining + D20.images.remaining + worflow.not.yet.assigned.images` = `r 171971 - (D40.images.remaining + D20.images.remaining + worflow.not.yet.assigned.images)`. -->

<!-- * 171971 - `r D40.images.remaining + D20.images.remaining + pageimages.to.be.treated.WPC` = `r 171971 - (D40.images.remaining + D20.images.remaining + pageimages.to.be.treated.WPC)`. -->


```{r EDFL_manicure, include=FALSE}

EDFL <- ServiceDetails %>%
  filter(grepl("Dickinson Family Library", ignore.case = TRUE, ActivityName) == TRUE) %>%
  filter(grepl("capture", ignore.case = TRUE, BillingType) == TRUE |
           grepl("scan", ignore.case = TRUE, BillingType) == TRUE) %>%
  filter(`PhotoduplicationDate (Day-Month-Year)` > start.measure.date)

class(EDFL$`PhotoduplicationDate (Day-Month-Year)`)

# --- #
EDFL["Date"] <- NA # Create MM/YY date column, to group by month
i <- 1
n <- nrow(EDFL)
while(i <= n){
  d <- paste(
    lubridate::month(EDFL$`PhotoduplicationDate (Day-Month-Year)`[i]),
    lubridate::year(EDFL$`PhotoduplicationDate (Day-Month-Year)`[i]),
    sep = "/")
  EDFL$Date[i] <- d
  i <- i + 1
}

# --- #
tmp <- EDFL %>%
#  filter(`PhotoduplicationDate (Day-Month-Year)` > start.measure.date) %>%
  group_by(Date) %>%
  summarise(ActivityName=unique(ActivityName),Quantity=sum(Quantity),PaymentAmount=sum(PaymentAmount))

summary.EDFL <- tmp ; rm(tmp)
summary.EDFL["RunningTotal"] <- NA
summary.EDFL["months.production.cumulative"] <- NA #
summary.EDFL["average.prod.month.cumulative"] <- NA
summary.EDFL$Date <- lubridate::as_date(summary.EDFL$Date,format="%m/%Y"); summary.EDFL$Date 
summary.EDFL <- summary.EDFL %>% arrange(Date)

i <- 1
n <- nrow(summary.EDFL)
while(i <= n){
  if(i == 1){
    rt <- summary.EDFL$Quantity[i]
    summary.EDFL$RunningTotal[i] <- as.numeric(rt)
    summary.EDFL$months.production.cumulative[i] <- time_length(summary.EDFL$Date[i] - start.measure.date,unit = "months")
    av <- summary.EDFL$RunningTotal[i] / summary.EDFL$months.production.cumulative[i]
    summary.EDFL$average.prod.month.cumulative[i] <- av
  } else {
    rt <- summary.EDFL$RunningTotal[i - 1] + summary.EDFL$Quantity[i]
    summary.EDFL$RunningTotal[i] <- as.numeric(rt)
    tl <- time_length(summary.EDFL$Date[i] - summary.EDFL$Date[i - 1],unit = "months")
    summary.EDFL$months.production.cumulative[i] <- summary.EDFL$months.production.cumulative[i - 1] + tl
    av <- summary.EDFL$RunningTotal[i] / summary.EDFL$months.production.cumulative[i]
    summary.EDFL$average.prod.month.cumulative[i] <- av
  }
  i <- i + 1
}
# ----- below under construction ----- #
int <- lubridate::interval(
  start.measure.date,
  max(summary.EDFL$Date)
  )

ds <- dseconds(int) ; ds # duration in seconds
period.measured.months <- max(summary.EDFL$months.production.cumulative) # duration in months

# ---- #

average.images.month <- sum(summary.EDFL$Quantity)/period.measured.months # AVERAGE images per month

```

```{r gannt, include=FALSE, eval=FALSE}

g <-DiagrammeR::mermaid("
  gantt
        dateFormat  YYYY-MM-DD
        title Adding GANTT diagram functionality to mermaid
        section A section
        Completed task            :done,    des1, 2014-01-06,2014-01-08
        Active task               :active,  des2, 2014-01-09, 3d
        Future task               :         des3, after des2, 5d
        Future task2               :         des4, after des3, 5d
        section Critical tasks
        Completed task in the critical line :crit, done, 2014-01-06,24h
        Implement parser and jison          :crit, done, after des1, 2d
        Create tests for parser             :crit, active, 3d
        Future task in critical line        :crit, 5d
        Create tests for renderer           :2d
        
        Add to mermaid                      :1d
        
")


# --- Gannt Header --- #
  gannt.h.df <- "YYYY-MM-DD"
  gannt.h.af <- "%b %y"
  gannt.h.ti <- "Dickinson Family Library image countdown"
  
  g.header <- paste0(
    "dateFormat ",gannt.h.df,"\n",
    "axisFormat ",gannt.h.af,"\n",
    "title ",gannt.h.ti,"\n"
  )
  
  # --- Gannt Section --- #

  sections.count <- length(
    unique(summary.EDFL$ActivityName)
  )

## TO DO  
## create a section name variable for the number of sections identified in sections.count
## populate the variables with each identified section name
  
g.s.name <- "section Images per month\n"
  
#g.s.name <- unique(summary.EDFL$ActivityName)[sections.count] # make a section name column?

# --- Write text file SINK --- #
gannt.file.name <- "gfile.txt"
file.remove(gannt.file.name)
sink(gannt.file.name,append = TRUE)
cat(g.header)
cat(g.s.name)
#sink() ; file.show("gfile.txt")
  
# --- Gannt tasks --- #

i <- 1
n <- nrow(summary.EDFL)
while(i <= n){
  tn_01 <- format.Date(paste0(summary.EDFL$Date[i]),"%b.%y")
  tn_02 <- paste0(",",prettyNum(summary.EDFL$RunningTotal[i],big.mark = ","))
  tn_03 <- "\t:"
  tn_04 <- paste0("task-",i,",",summary.EDFL$Date[i],",4w")
  t_id <- paste(tn_01,tn_02,tn_03,tn_04, sep=" ")
  #sink("gfile.txt",append = TRUE)
  cat(paste0("\n",t_id))
  i <- i + 1
}
sink() ; file.show(gannt.file.name)
  
  
```

```{r stackedBar,include=FALSE}

df.tmp <- summary.EDFL
df.tmp["TargetImageCount"] <- images.remaining.as.of.start.measure.date
# DELETE df.tmp["AverageMonthlyImageProduction"] <- NA
df.tmp["percentCompleted"] <- df.tmp$RunningTotal/df.tmp$TargetImageCount
df.progressMeter <- df.tmp

i <- 1
n <- nrow(df.progressMeter)
while (i <= n) {
  if (i == 1) {
    df.progressMeter$TargetImageCount[i] <-
      images.remaining.as.of.start.measure.date - df.progressMeter$RunningTotal[i]
  }
  else {
    df.progressMeter$TargetImageCount[i] <-
      df.progressMeter$TargetImageCount[i - 1] - df.progressMeter$Quantity[i]
  }
  i <- i + 1
}  

names(df.progressMeter)
bar.progressMeter <-
  plot_ly(
    df.progressMeter,
    x = ~Date,
    y = ~RunningTotal,
    type = "bar",
    color = "rgb(142,1,82,0)",
    name = "images produced"
  ) %>%
  add_trace(y = ~TargetImageCount, name = "Estimated images remaining", marker = list(color = "rgb(106,61,254)")) 

# bar.progressMeter <- bar.progressMeter %>%
#  add_trace(y = ~TargetImageCount, name = "Estimated total images",marker = list(color = "rgb(231,41,138)"))

bar.progressMeter <- bar.progressMeter %>%
  layout(
    title = "Progress Meter",
    yaxis = list(title = "image count",
                 tickformat=","), # comma separator for thousands
    xaxis = list(title = "",
                 tickformat ="%b %Y"), # date formatted
    plot_bgcolor = '#e5ecf6',
    barmode = "stack"
  ) 

```

```{r scatterActual, include=FALSE}
##################################
##### This plot not deployed #####
##################################
df.tmp <- summary.EDFL
df.tmp["TargetImageCount"] <- images.remaining.as.of.start.measure.date
# DELETE df.tmp["AverageMonthlyImageProduction"] <- average.images.month 
df.tmp["percentCompleted"] <- df.tmp$RunningTotal/df.tmp$TargetImageCount
df.progressMeter <- df.tmp

i <- 1
n <- nrow(df.progressMeter)
while (i <= n) {
  if (i == 1) {
    df.progressMeter$TargetImageCount[i] <-
      images.remaining.as.of.start.measure.date - df.progressMeter$RunningTotal[i]
  }
  else {
    df.progressMeter$TargetImageCount[i] <-
      df.progressMeter$TargetImageCount[i - 1] - df.progressMeter$Quantity[i]
  }
  i <- i + 1
}  

names(df.progressMeter)
line.progressMeter <-
  plot_ly(
    df.progressMeter,
    x = ~Date,
    y = ~ RunningTotal,
    type = "scatter",
    connectgaps = TRUE,
    mode = "lines",
    color = "#184C78",
    marker = list(color = "#02735E"),
    name = "images completed"
  )

# add_trace(y = ~ images.remaining.as.of.start.measure.date, name = "Estimated images remaining", marker = list(color = "rgb(106,61,254)"))

line.progressMeter <- line.progressMeter %>%
  add_trace(y = ~TargetImageCount, name = "Estimated images remaining",marker = list(color = "#D92525"))

line.progressMeter <- line.progressMeter %>%
  layout(
    title = "",
    yaxis = list(title = "image count"),
    xaxis = list(title = "Date"),
    plot_bgcolor = '#e5ecf6'
    #barmode = "stack"
  )

```

```{r projectingFinish, include=FALSE}

remaining <- images.remaining.as.of.start.measure.date - max(summary.EDFL$RunningTotal)
remainingMonths <- remaining / average.images.month
projectedEndDate <- max(summary.EDFL$Date) + lubridate::dmonths(x = remainingMonths)
targetEndDate <- as.Date(
  format.Date("2027-06-30","%Y-%m-%d")
  ); class(targetEndDate)

lastMonthMeasured <- max(summary.EDFL$Date) ; class(lastMonthMeasured)

months.to.go.goal <- lubridate::time_length(targetEndDate -lastMonthMeasured,unit = "months")

monthly.target <- remaining/months.to.go.goal

batches.completed <- nrow(summary.EDFL)
format.Date(min(summary.EDFL$Date),"%B %Y")
prettyNum(sum(summary.EDFL$Quantity),big.mark = ",")

prettyNum(round(average.images.month,digits = 0), big.mark = ",")

prettyNum(remaining, big.mark = ",")
prettyNum(round(av,digits = 0), big.mark = ",")
format.Date(projectedEndDate, "%B %d, %Y")
format.Date(targetEndDate, "%B %d, %Y")
prettyNum(round(monthly.target,digits = 0), big.mark = ",")

```

```{r scatterProjected, include=FALSE, eval=FALSE}

df.tmp <- summary.EDFL
df.tmp["TargetImageCount"] <- images.remaining.as.of.start.measure.date
# DELETE df.tmp["AverageMonthlyImageProduction"] <- average.images.month 
df.tmp["percentCompleted"] <- df.tmp$RunningTotal/df.tmp$TargetImageCount

df.progressMeter <- df.tmp

i <- 1
n <- nrow(df.progressMeter)
while (i <= n) {
  if (i == 1) {
    df.progressMeter$TargetImageCount[i] <-
      images.remaining.as.of.start.measure.date - df.progressMeter$RunningTotal[i]
  }
  else {
    df.progressMeter$TargetImageCount[i] <-
      df.progressMeter$TargetImageCount[i] - df.progressMeter$RunningTotal[i]
  }
  i <- i + 1
}
## ---------------------------- ##
######### projection row #########
names(df.progressMeter)
date.1 <- as.Date("2023-06-08")
ActivityNAme.2 <- paste0(unique(df.progressMeter$ActivityName),"--PROECTED")
Quantity.3 <- df.progressMeter$TargetImageCount[1] - df.progressMeter$RunningTotal[nrow(df.progressMeter)]
PaymentAmount.4 <- 0
RunningTotal.5 <- sum(df.progressMeter$Quantity)
m <- time_length(as.Date(projectedEndDate) - df.progressMeter$Date[1], unit = "months") + max(df.progressMeter$months.production.cumulative)
months.production.cumulative.6 <- as.numeric(m)
average.prod.month.cumulative.7 <- df.progressMeter$average.prod.month.cumulative[nrow(df.progressMeter)]
TargetImageCount.8 <-  df.progressMeter$TargetImageCount[1] - df.progressMeter$RunningTotal[nrow(df.progressMeter)]
percentCompleted.9 <- 1

df.projection <- data.frame(
  as.Date(date.1),
  as.character(ActivityNAme.2),
  as.numeric(Quantity.3),
  as.numeric(PaymentAmount.4),
  as.numeric(RunningTotal.5),
  as.numeric(months.production.cumulative.6),
  as.numeric(average.prod.month.cumulative.7),
  as.numeric(TargetImageCount.8),
  as.numeric(percentCompleted.9)
)

colnames(df.projection) <- names(df.progressMeter)
# so confusing
df.projection$RunningTotal[nrow(df.projection)] <- sum(df.progressMeter$Quantity) + df.projection$Quantity[nrow(df.projection)]

names(df.progressMeter)
line.progressMeter <-
  plot_ly(
    df.progressMeter,
    x = ~Date,
    y = ~ RunningTotal,
    type = "scatter",
    connectgaps = TRUE,
    mode = "lines",
    color = "#184C78",
    marker = list(color = "#02735E"),
    name = "images completed"
  )

line.progressMeter <- line.progressMeter %>%
  add_trace(y = ~TargetImageCount, name = "Estimated images remaining",marker = list(color = "#D92525"))

line.progressMeter <- line.progressMeter %>%
  layout(
    title = "",
    yaxis = list(title = "image count"),
    xaxis = list(title = "Date"),
    plot_bgcolor = '#e5ecf6'
    #barmode = "stack"
  )

###################

period.projected.months.remaining = months(integer(remainingMonths))
time_length(period.projected.months.remaining, unit="months")

start <- ymd(Sys.Date())

start %m+% months(60)


```

```{r imagesPerMonth, include=FALSE, eval=TRUE}

#### HERE ###

df.tmp <- summary.EDFL
df.tmp["TargetImageCount"] <- images.remaining.as.of.start.measure.date
# DELETE df.tmp["AverageMonthlyImageProduction"] <- average.images.month 
df.tmp["percentCompleted"] <- df.tmp$RunningTotal/df.tmp$TargetImageCount

df.progressMeter <- df.tmp

names(df.progressMeter)
imagesPerMonth.progressMeter <-
  plot_ly(
    df.progressMeter,
    x = ~Date,
    y = ~ Quantity,
    type = "scatter",
    connectgaps = TRUE,
    mode = "markers",
    # color = "#184C78",
    # marker = list(color = "#02735E"),
                   marker = list(size = 10,
                             color = 'rgba(255, 182, 193, .9)',
                             line = list(color = 'rgba(152, 0, 0, .8)',
                                         width = ~Quantity/200)),
    name = "images per month"
  )

imagesPerMonth.progressMeter <- imagesPerMonth.progressMeter %>%
  layout(
    title = "Monthly DRS deposit log",
    yaxis = list(title = "images per month",
                 tickformat = ",",
                 hoverformat = ","), # comma separator for thousands
    xaxis = list(title = "",
                 type ="date",
                 tickformat = "%b %Y"), # date format specified
    plot_bgcolor = '#e5ecf6'
  )

```


```{r DELETE_projectingFinish, include=FALSE, eval=FALSE}

remaining <- images.remaining.as.of.start.measure.date - max(summary.EDFL$RunningTotal)
remainingMonths <- remaining / average.images.month
projectedEndDate <- max(summary.EDFL$Date) + lubridate::dmonths(x = remainingMonths)
targetEndDate <- as.Date(
  format.Date("2026-06-30","%Y-%m-%d")
  ); class(targetEndDate)

lastMonthMeasured <- max(summary.EDFL$Date) ; class(lastMonthMeasured)

months.to.go.goal <- lubridate::time_length(targetEndDate -lastMonthMeasured,unit = "months")

monthly.target <- remaining/months.to.go.goal

batches.completed <- nrow(summary.EDFL)
format.Date(min(summary.EDFL$Date),"%B %Y")
prettyNum(sum(summary.EDFL$Quantity),big.mark = ",")

prettyNum(round(average.images.month,digits = 0), big.mark = ",")

```

## Increasing production

In June 2023, Houghton Library requested increased imaging production for the *[Dickinson Family Library](https://id.lib.harvard.edu/ead/hou00321/catalog)* project.

Through consultation, testing and evaluation, Houghton and Imaging Services revised the sorting criteria used to determine which books require specialized handling and photography from those well-matched to our standardized, higher-production, photography service. **The updated sorting criteria dramatically increased the proportion of books routed to the higher-throughput service.**

Per Christine Jacobson, `r start.measure.date`, an **estimated `r prettyNum(images.remaining.as.of.start.measure.date,big.mark=",")` page-images remained**.

Post-`r start.measure.date`, **Imaging Services has completed `r batches.completed` batches, with page-images totaling `r prettyNum(sum(summary.EDFL$Quantity),big.mark = ",")`--an average `r prettyNum(round(average.images.month,digits = 0), big.mark = ",")` per month**.

### Estimating remaining volumes and page-images, per CJ, 06/27/2024

* Studio (D40) designated titles: `r prettyNum(D40.images.remaining, big.mark = ",")` page-images.
* Lab (D20) desginated titles: `r prettyNum(D20.images.remaining, big.mark = ",")` page-images.
* D20- & D40-designated items that need to be treated: `r prettyNum(pageimages.to.be.treated.WPC, big.mark = ",")` page-images.
* To-be-designated items: `r prettyNum(worflow.not.yet.assigned.images, big.mark = ",")` page-images
* Total number of images, estimated: `r prettyNum(images.remaining.as.of.start.measure.date, big.mark = ",")`

### At our current production rate

With **`r prettyNum(remaining, big.mark = ",")` images remaining**, and our current **production rate of `r prettyNum(round(av,digits = 0), big.mark = ",")` per month**, our **projected project completion date is `r format.Date(projectedEndDate, "%B %d, %Y")`**.


`r imagesPerMonth.progressMeter`

---

### Targeting a date for completing the project

Alternatively, if we set a **goal of completing the project on `r format.Date(targetEndDate, "%B %d, %Y")`**, our production rate would need to be **`r prettyNum(round(monthly.target,digits = 0), big.mark = ",")` images per month**.

---

`r bar.progressMeter`


```{r tail, include=FALSE}
lastRevised <- timestamp(pre="last revised: ",suffix = "")
file.copy(from = "EDFL-tracking.html", to = "index.html",overwrite = TRUE)
browseURL("https://comstock.github.io/EDFL/")
```
 ---
 
  <center><small>`r lastRevised`</small></center>
  <br /><br />